Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic: adapted to CHOP input format

### 2022-04-01 metanalysis_visualization/manuscript_Figures.Rmd

>>>>

```{r}
patient_count_psy_period_psy_all <- patient_count_psy_period_psy_all %>%
  left_join( country_map )

ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_all.png", height = 20, width = 32, units = "cm")
```

### 2022-04-01 psy_peds_3_CHOP.Rmd

```{r}
# cut-off dates used in the analysis, these should not be changed
history_start_date <- as.Date("2019-01-01")
history_end_date <- as.Date("2021-05-31")
pandemic_start_date <- as.Date("2020-03-15")
start_date_plots <- as.Date("2019-01-15")
end_date_plots <- as.Date("2021-05-01")
```

@@

@@

save( count_icd, 
      ratios_patients_with_without_psy,
      patient_count_psy_period_psy,
      patient_count_psy_period_psy_clear,
      bootstrapped_coefficients_df,
      bootstrapped_fitted_df,
      quantile_bootstrapped_fitted,
      perc_disorder_group,
      patients_hospitalized_agg_sex_perc,
      mental_codes_qc_output,
      table1,
      file = paste0("../output/CHOP/peds_psy_aggResults_", site, ".RData"))

>>>>

```{r}
# cut-off dates used in the analysis, these should not be changed
history_start_date <- as.Date("2019-01-01")
history_end_date <- as.Date("2021-05-31")
pandemic_start_date <- as.Date("2020-03-15")
start_date_plots <- as.Date("2019-01-15")
end_date_plots <- as.Date("2021-06-01")
```

@@

# Add the length of hospitalization data
```{r}
length_hospitalisation_values <- read.delim("../output/CHOP/length_hospitalization_formated.txt") %>%
  mutate( period = tolower( Period )) %>%
  select(  len_hospitalisation = Hospitalization.Length,  siteid, period)
```

@@

save( count_icd, 
      ratios_patients_with_without_psy,
      patient_count_psy_period_psy,
      patient_count_psy_period_psy_clear,
      bootstrapped_coefficients_df,
      bootstrapped_fitted_df,
      quantile_bootstrapped_fitted,
      perc_disorder_group,
      patients_hospitalized_agg_sex_perc,
      mental_codes_qc_output,
      length_hospitalisation_values,
      table1,
      file = paste0("../output/CHOP/peds_psy_aggResults_", site, ".RData"))
